Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-05 paperIEEE.tex
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@103 db7c848b-7755-4df2-b763-8796797afa52

\begin{compactdesc}
\item[Split Mode] configures the tile layout: horizontal or vertical stripes,
and 2D, an binary tree split alternating the split axis on each level, resulting
in compact 2D tiles.
\item[Damping] reduces frame-to-frame oscillations. The equal load distribution
within the region of interest assumed by the load equalizer is in reality not
equal, causing the load balancing to overshoot. Damping is a normalized scalar
defining how much of the computed delta from the previous position is applied to
the new split.
\item[Resistance] eliminates small deltas in the load balancing step. This might
help the application to cache visibility computations since the frustum does not
change each frame.
\item[Boundaries] define the modulo factor in pixels onto which a load split may
fall. Some rendering algorithms produce artefacts related to the OpenGL raster
position, e.g., screen door transparency, which can be eliminated by aligning
the boundary to the pixel repetition. Furthermore, some rendering algorithms are
sensitive to cache alignments, which can again be exploited by chosing the
corresponding boundary.
\end{compactdesc}

@@

This figure gives an impression of how individual modes perform on heterogeneous systems. In this case the tree equalizer performs best (\fig{fEqualizers} (left)), as it allows us to a priori define how much {\em usage} it should make of individual rendering nodes, in accordance with the expected load / the available compute resources. \fig{fEqualizers} (right), on the other hand, illustrates how decomposition modes perform on a system where compute resources fluctuate randomly every frame, as can arguably be the case for cloud-based applications. For this scenario tile equalizer seems best suited, as it performs load balancing implicitly and does not assume coherence of available resources between frames.

>>>>

\begin{compactdesc}
\item[Split Mode] configures the tile layout: horizontal or vertical stripes,
and 2D, a binary tree split alternating the split axis on each level, resulting
in compact 2D tiles.
\item[Damping] reduces frame-to-frame oscillations. The equal load distribution
within the region of interest assumed by the load equalizer is in reality not
equal, causing the load balancing to overshoot. Damping is a normalized scalar
defining how much of the computed delta from the previous position is applied to
the new split.
\item[Resistance] eliminates small deltas in the load balancing step. This might
help the application to cache visibility computations since the frustum does not
change each frame.
\item[Boundaries] define the modulo factor in pixels onto which a load split may
fall. Some rendering algorithms produce artefacts related to the OpenGL raster
position, e.g., screen door transparency, which can be eliminated by aligning
the boundary to the pixel repetition. Furthermore, some rendering algorithms are
sensitive to cache alignments, which can again be exploited by chosing the
corresponding boundary.
\end{compactdesc}

@@

This figure gives an impression of how individual modes perform on heterogeneous systems. In this case the tree equalizer performs best (\fig{fEqualizers} (left)), as it allows us to a priori define how much {\em usage} it should make of individual nodes, i.e., bias the allocation of rendering time, in accordance with the expected load / the available compute resources. \fig{fEqualizers} (right), on the other hand, illustrates how the tested decomposition modes perform on a system where compute resources fluctuate randomly every frame, as can arguably be the case for, e.g., cloud-based applications. \FIXME{Should we only mention this in discussion?} For this scenario tile equalizer seems best suited, as it performs load balancing implicitly and does not assume coherence of available resources between frames.
